---
title: "Assignment 9"
author: "Penelope Weekes"
date: "2023-01-30"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---
#### Using a `for` loop and an `if` statement, write a function to calculate the number of zeroes in a numeric vector. Before entering the loop, set up a vector of integers with some zero values. Then, set up a counter variable `counter <- 0`. Inside the loop, add 1 to counter each time you have a zero in the vector. Finally, use `return(counter)` for the output.

```{r}
myVec <- sample(rep(c(0:5), each = 7))
counter <- 0

for (i in 1:length(myVec)) {
  if (myVec[i]==0) {counter <- counter + 1}
}

print(myVec)
print(counter)
```


#### Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number.

```{r}
my_matrix <- function(x = NULL, y = NULL) {
  m <- matrix(nrow=x,ncol=y,byrow=TRUE)
  for(i in 1:x){
  for(j in 1:y){
    m[i,j] <- i * j
  }
  }
  return(m)
}
my_matrix(3, 6)
```


#### Use a `for` loop to repeat your previous functions from Weekly Assignment 2 (which simulate a data frame and extract a p-value) 100 times. Store the results in a data frame that has 1 column indicating the replicate number and 1 column for the p-values (a total of 2 columns and 100 rows).

```{r}
my_function <- function(means=c(10,45), stdevs=c(1.5,2)){
  dframe <- data.frame(Type = c(rep("Control", 25), rep("Treatement", 25)), 
                       Value = c(rnorm(25, 10, 1.5), rnorm(25, 45, 2) ))

  return(dframe)
}

my_variable <- my_function()

p_aov <- function(p = my_function){
  
 my_aov <- aov(Value ~ Type, data = my_variable)
 p <- summary(my_aov)[[1]][["Pr(>F)"]][1]
  
  return(p)
}
p_aov()

df <- data.frame(iVal = NA, pVal = NA)

for (i in 1:100){
  my_variable <- my_function()
  pVal <- p_aov(my_variable)
  iVal <- i
  df[i,1] <- iVal
  df[i,2] <- pVal
}

print(df)


```

