---
title: "Weekly Assignment 2 Annotated"
author: "Penelope Weekes"
date: "2023-01-26"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---
# Creating Functions

#### 1. Create a function that returns a data frame with 2 columns (named “Type” and “Value”) and 50 rows/observations.
  - The first column should have “Control” as the first 25 observations and “Treatment” as the second half of observations.
  - The second column should have the first 25 values as random and normally distributed with a mean of 10 and standard deviation of 1.5. The next 25 values of the second column should be random and normally distributed with a mean of 45 and standard deviation of 2.
  - The arguments of your function should be the two means of the random normal numbers.
  - The body of the function can be a single line of code (if you want a challenge) or broken up into multiple code blocks.
```{r}
## could have set seed before (for reproducibility)
my_function <- function(means=c(10,45), stdevs=c(1.5,2)){
  dframe <- data.frame(Type = c(rep("Control", 25), rep("Treatement", 25)), 
                       Value = c(rnorm(25, mean=means[1], sd=stdevs[1]), 
                                 rnorm(25, mean=means[2], sd=stdevs[2]) )) 

## changed to make the mean/sd equal to the variables in the argument so that
## I could run the simulated data function with new values for the means

  return(dframe)
}

my_function()

my_function(means=c(12,14), stdevs=c(10, 8))
```
#### Save your new function’s output as a variable, and view the first 6 rows of the data frame.
```{r}
my_variable <- my_function()

head(my_variable)

## good!
```
#### Write a line of code that displays a summary of your ANOVA.

```{r}
my_aov <- aov(Value ~ Type, data = my_variable)
summary(my_aov)

## nice
```
#### Finally create a function that uses a data frame as its input and returns only the p-value of an ANOVA summary table. Write your code in such a way that you can use any simulated data set with two columns as your ANOVA function’s argument.

```{r}
p_aov <- function(p = my_variable){ ## changed to use data instead of my_function
  
 my_aov <- aov(Value ~ Type, data = p) ## changed to use my argument
 p <- summary(my_aov)[[1]][["Pr(>F)"]][1]
  
  return(p)
}
p_aov()


```
